---
title: 'Lab 06: Simulation-based inference'
author: ''
date: ''
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
subtitle: 'Due: Sat, Mar 13 at 11:59pm ET'
---

```{r set_up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
set.seed(352790)
```

# Packages

```{r load_packages}
library(tidyverse)
library(infer)
``` 

# Data

In this lab, you'll work with a couple of datasets.

The `ToothGrowth` dataset can be loaded into R with `data("ToothGrowth)`. It
contains data on the length of odontoblasts (cells responsible for tooth growth) 
in 60 guinea pigs. Each animal received one of three dose levels of vitamin C 
(0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice (`OJ`) or 
ascorbic acid (`VC`) (a form of vitamin C and coded as VC). For the purposes of 
this lab, we will ignore the `dose` variable.

```{r load_tooth_data}
data("ToothGrowth")
```

The second dataset is a subset of `gss_cat` from the `forcats` package. It
contains categorical variables from the General Social Survey in 2014.

```{r load_gss_data, echo=TRUE}
gss_2014 <- gss_cat %>% 
  filter(year == 2014)
```

# Exercises

## Exercise 1

```{r ex_1}
```





# References

"Infer - Tidy Statistical Inference". Infer.Netlify.App, 2021, https://infer.netlify.app/index.html.